\pdftitle

### 2018-07-26 nips_2018_author_response.tex
update text and scripts

\iffalse
\usepackage[shortlabels,inline]{enumitem}
\SetEnumitemKey{para}{itemindent=\parindent,leftmargin=0pt,listparindent=\parindent,parsep=0pt,itemsep=\topsep}
% \begin{asparaenum} = \begin{enumerate}[para]
% \begin{inparaenum} = \begin{enumerate*}
\setlist[enumerate,2]{label=\alph*.}
\setlist[enumerate]{leftmargin=\parindent}
\setlist[itemize]{leftmargin=\parindent}
\setlist[description]{leftmargin=\parindent}
\fi
%% With euler font cursive for Greek letters - the [1] means 100% scaling
\DeclareFontFamily{U}{egreek}{\skewchar\font'177}%
\DeclareFontShape{U}{egreek}{m}{n}{<-6>s*[0.95]eurm5 <6-8>s*[0.95]eurm7 <8->s*[0.95]eurm10}{}%
\DeclareFontShape{U}{egreek}{m}{it}{<->s*[0.95]eurmo10}{}%
\DeclareFontShape{U}{egreek}{b}{n}{<-6>s*[0.95]eurb5 <6-8>s*[0.95]eurb7 <8->s*[0.95]eurb10}{}%
\DeclareFontShape{U}{egreek}{b}{it}{<->s*[0.95]eurbo10}{}%
\DeclareSymbolFont{egreeki}{U}{egreek}{m}{it}%
\SetSymbolFont{egreeki}{bold}{U}{egreek}{b}{it}% from the amsfonts package
\DeclareSymbolFont{egreekr}{U}{egreek}{m}{n}%
\SetSymbolFont{egreekr}{bold}{U}{egreek}{b}{n}% from the amsfonts package
% Take also \sum, \prod, \coprod symbols from Euler fonts
\DeclareFontFamily{U}{egreekx}{\skewchar\font'177}
\DeclareFontShape{U}{egreekx}{m}{n}{%
       <-7.5>s*[0.9]euex7%
    <7.5-8.5>s*[0.9]euex8%
    <8.5-9.5>s*[0.9]euex9%
    <9.5->s*[0.9]euex10%
}{}
\DeclareSymbolFont{egreekx}{U}{egreekx}{m}{n}
\DeclareMathSymbol{\sumop}{\mathop}{egreekx}{"50}
\DeclareMathSymbol{\prodop}{\mathop}{egreekx}{"51}
\DeclareMathSymbol{\coprodop}{\mathop}{egreekx}{"60}
\makeatletter
\def\sum{\DOTSI\sumop\slimits@}
\def\prod{\DOTSI\prodop\slimits@}
\def\coprod{\DOTSI\coprodop\slimits@}
\makeatother

@@

\begin{document}
We thank the reviewers for their analysis and suggestions. We would like to
reply to specific points:
\begin{enumerate}
\item We agree with Reviewer 3 that the paper emphasizes some philosophical
  aspects; intentionally so. Sadly we can't make all kinds of readers
  happy; a choice of audience is necessary. As readers ourselves we
  appreciate when a paper begins by asking: \enquote{What is the question?
    is it possible to translate it into a mathematical problem? which
    principles can we use to make such translation?}. There are papers that
  develop very refined mathematical techniques but leave us unsatisfied,
  with the lingering question \enquote{why are we doing this?}. This is the
  reason why we try to emphasize these kinds of questions. But we are sure
  that part of the NIPS audience will appreciate this emphasis.

\item We also agree with Reviewer 3 that the main formulae of the paper,
  (17) and (19), probably have little experimental use today. But the point
  they make is important:
  \begin{itemize}
  \item the Reviewer says \enquote{the differences between the sample level
      and population level distribution seem minor} -- but we could not
    have known this, if we hadn't faced the whole problem and derived a
    formula showing that the difference is minor;
  \item the sample-level distribution is actually \emph{less} entropic. By
    lifting the constraints to the population level, the maximum-entropy
    principle allows us to explore even \emph{more entropic} sample
    distributions than those allowed by a direct application at the sample
    level. Thus this approach agrees with the \enquote{maximum entropy}
    spirit. -- These points should be mentioned, of course, in an amended
    version of the paper.
  \item 
  \end{itemize}

>>>>

\usepackage[shortlabels,inline]{enumitem}
\SetEnumitemKey{para}{itemindent=\parindent,leftmargin=0pt,listparindent=\parindent,parsep=0pt,itemsep=\topsep}
% \begin{asparaenum} = \begin{enumerate}[para]
% \begin{inparaenum} = \begin{enumerate*}
\setlist[enumerate,2]{label=\alph*.}
\setlist[enumerate]{leftmargin=1.5em}
\setlist[itemize]{leftmargin=1.5em}
\setlist[description]{leftmargin=\parindent}

%% With euler font cursive for Greek letters - the [1] means 100% scaling
\DeclareFontFamily{U}{egreek}{\skewchar\font'177}%
\DeclareFontShape{U}{egreek}{m}{n}{<-6>s*[0.95]eurm5 <6-8>s*[0.95]eurm7 <8->s*[0.95]eurm10}{}%
\DeclareFontShape{U}{egreek}{m}{it}{<->s*[0.95]eurmo10}{}%
\DeclareFontShape{U}{egreek}{b}{n}{<-6>s*[0.95]eurb5 <6-8>s*[0.95]eurb7 <8->s*[0.95]eurb10}{}%
\DeclareFontShape{U}{egreek}{b}{it}{<->s*[0.95]eurbo10}{}%
\DeclareSymbolFont{egreeki}{U}{egreek}{m}{it}%
\SetSymbolFont{egreeki}{bold}{U}{egreek}{b}{it}% from the amsfonts package
\DeclareSymbolFont{egreekr}{U}{egreek}{m}{n}%
\SetSymbolFont{egreekr}{bold}{U}{egreek}{b}{n}% from the amsfonts package
% Take also \sum, \prod, \coprod symbols from Euler fonts
\DeclareFontFamily{U}{egreekx}{\skewchar\font'177}
\DeclareFontShape{U}{egreekx}{m}{n}{%
       <-7.5>s*[0.9]euex7%
    <7.5-8.5>s*[0.9]euex8%
    <8.5-9.5>s*[0.9]euex9%
    <9.5->s*[0.9]euex10%
}{}
\DeclareSymbolFont{egreekx}{U}{egreekx}{m}{n}
\DeclareMathSymbol{\sumop}{\mathop}{egreekx}{"50}
\DeclareMathSymbol{\prodop}{\mathop}{egreekx}{"51}
\DeclareMathSymbol{\coprodop}{\mathop}{egreekx}{"60}
\makeatletter
\def\sum{\DOTSI\sumop\slimits@}
\def\prod{\DOTSI\prodop\slimits@}
\def\coprod{\DOTSI\coprodop\slimits@}
\makeatother

@@

\begin{document}
We thank the reviewers for their analysis, appreciative words, and suggestions.

\textbf{Reviewer 1}
\begin{enumerate}
\item It would be interesting to use the frequency distribution of the
  sample activity, measured in the recording, as a constraint, equivalent
  to $n$ moment constraints. In fact, using it at the population level is
  less questionable than using at the sample level (activities with zero
  frequencies lead to zeroes in the maximum-entropy distribution, and these
  are unreasonable because the sample size is much smaller than the
  state-space size. This indicates that maximum-entropy is used beyond its
  range of validity). Its use, however, addresses a different question than
  the one discussed in our introduction, namely to define and measure
  \enquote{cooperativity} by comparing maximum-entropy distributions
  constructed from different numbers of moments.
\item Unfortunately the reviewer forgot the bibliographic reference to Tkacik et al
  2012. We'd like to read that paper.
\item It's true, we forgot to discuss how the population-level application
  solves the sample-size-dependence of maximum-entropy results pointed out in
  previous literature. This should be addressed in an amended version of
  the paper.
\end{enumerate}

\medskip

\textbf{Reviewer 2}
\begin{enumerate}
\item We agree that the comparison with other approaches is important. But
  we believe that it's also important to carefully examine (1) the question
  we're asking, and (2) which first principles, if any, can be used to
  translate it into a mathematical problem. A lot of literature develops
  very refined -- though often ad hoc -- mathematical techniques; and yet
  it leaves us unsatisfied, with the lingering question \enquote{why were
    we doing this?}. This is the reason for our long introductory
  discussion about the problem and the first principles that can be used to
  address it.
\item Regarding the effect of correlations on the result: the original
  question is how \enquote{cooperativity} can be related to the measured
  correlations, or defined in terms of them. The method is devised to give
  one answer to this question; see the \enquote{protocol} 1--3 in the
  Introduction. The crucial point is that there is no underlying
  distribution; the point of the method is to construct it for us.
\item We agree that there are many approaches in the literature. In the
  literature we have explored we've seen very little use of the basic
  sampling formulae presented in our paper. Honestly this surprised us,
  because they're surely essential even in a very basic analysis of the data.
\end{enumerate}

\medskip

\textbf{Reviewer 3}
\begin{enumerate}
\item We also agree with Reviewer 3 that the main formulae of the paper,
  (17) and (19), probably have little experimental use today. But the point
  they make is important:
  \begin{itemize}
  \item the Reviewer says \enquote{the differences between the sample level
      and population level distribution seem minor} -- but we could not
    have known this, if we hadn't faced the whole problem and derived a
    formula showing that the difference is minor;
  \item the sample-level distribution is actually \emph{less} entropic. By
    lifting the constraints to the population level, the maximum-entropy
    principle allows us to explore even \emph{more entropic} sample
    distributions than those allowed by a direct application at the sample
    level. Thus this approach agrees with the \enquote{maximum entropy}
    spirit. -- These points should be mentioned, of course, in an amended
    version of the paper.
  \item 
  \end{itemize}
\item We agree with Reviewer 3 that the paper emphasizes some philosophical
  aspects; intentionally so. Sadly we can't make all kinds of readers
  happy; a choice of audience is necessary. As readers ourselves we
  appreciate when a paper begins by asking: \enquote{What is the question?
    is it possible to translate it into a mathematical problem? which
    principles can we use to make such translation?}. There are papers that
  develop very refined mathematical techniques but leave us unsatisfied,
  with the lingering question \enquote{why are we doing this?}. This is the
  reason why we try to emphasize these kinds of questions. But we are sure
  that part of the NIPS audience will appreciate this emphasis.
